Predicting sales of newly published books

### 2015-10-22 paper.tex
changing the type of graphics (from 3D-bars to line plot grouped by color)
updating Tables of Results (16-vars)
fixing&improving the text, tanking into account some comments (thanks)

Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager can eventually 
take them into account \cite{Armstrong2001,SThomassey2014}. 
                                % ¿Esto también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ
                                % [Pedro] esto iba referido a la Industria Editorial.
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they
                                % do? What are the results?

In this research, the problem of how many books should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}}.
The company's expert sales managers analyzed historical data 
and applied their knowledge using external variables to calculate
appropriate predictions, for example, increasing or decreasing the 
sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.

%In any case, in general companies usually use a forecasting model and then, an expert applies his knowledge, as the company might require an interpretable and understandable model.

However, carrying out the analysis and forecasting process as described,
may lead to an imprecise analysis and may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is large, and even, different experts can reach different
predictions from the same data set \cite{ChingChin2010,Sanders1994}.

@@

This is the new book sales forecasting case, for which no historical data 
to make predictions \cite{ChingChin2010,FaderHardie2005,Madsen2008} is available
and only some descriptive variables relative to the new unpublished-book are available.

@@

The main issue of this paper is to forecast sales for 
unpublished books for which no historical data is available, just some
descriptive variables relative to the new book. In order to do that,
training data includes historical sales data for all books published
in Spain for several years, including those descriptive variables. 
%
%%% Principio de párrafos a eliminar o mover a estado del arte.
%Después de esto no sé si merece la pena dejar este párrafo.
Forecasting sales of new books is a problem with issues 
such as dealing with limited data, finding adequate forecasting methods and 
selecting the best method to use \cite{ChingChin2010}. % He cambiado
                                % esto, pero sigue sin decir
                                % absolutamente nada. "The problem"
                                % tiene que describir el problema: qué
                                % queremos hacer, qué tenemos - JJ

% Este párrafo o se borra o se traslada al estado del arte. Aquí hay
% que contar cuál es el problema y qué se tiene. No se puede volver a
% repetir lo de antes.
In the case of already published books, available historical data might help 
to generate predictive models.
However, in the case of new books there is no historical data to define patterns, 
and only some descriptive data about the new book is available. 
%FERGU: data es plural. is->are   ...a mí me suena bien con "is"   ¡una segunda opinión!   ;)
In these cases not any forecasting method can be used \cite{Madsen2008,ChernWSF15}.

% Vale, más issues. Este párrafo también puede quedar fuera. Ya has
% dicho que no se puede usar la serie histórica.
An additional issue is the difficulty to compare our model with classical 
forecasting methods, such as time series prediction methods, since books 
do not have specific sales time series.

Throughout this research, we collaborated with the company Trevenque Editorial, %\footnote{{\tt http://editorial.trevenque.es}}, 
a company that provides management systems and services for libraries, publishers 
and distributors. % Esto tampoco viene a cuento. Se dice en la intro o
                  % se cuenta como gente que nos ha proporcionado los
                  % datos y nos contrató para hacerlo.

Trevenque company, whose expert manager advised this research,
provided %FERGU: los párrafos anteriores son un poco dispersos, puedes
         %quitar los puntos y aparte y agruparlos por temas (por
         %ejemplo, todo lo de Trevenque debería de ir en un párrafo) 
% O borrarlos - JJ
%% Fin de párrafos a eliminar.
This initial data set, provided in the framework of a contract by
Trevenque Editorial, included 3159 books, and included descriptive information 
for each book, such as price, points of sale, subject, publisher, sales, returns, 
among other information.
Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
each book.

@@

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	      & MAE 		& RMSE 		& RAE (\%) & RRSE (\%) 		\\
\hline
  M5P 		& 23.13 $\pm$ 4.22    & 197.48  & 577.28  & 35.21    & 41.85  \\
\hline
  LR 		  & 3327.87 $\pm$ 607.58& 247.22 & 561.67  & 44.08    & 40.71    \\
\hline
  SVM 		& 5425.68 $\pm$ 990.59& 215.69  & 574.76  & 38.46    & 41.66  \\
\hline
  kNN 		& 0.02 $\pm$ 0.00     & 302.07 	& 924.94 	& 53.86 	 & 67.05 	\\
\hline
  MLP 		& - 	  & - 	& - 	& - 	& - 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the original dataset (16 variables per book). 
    In this case, due to the categorial variables, the MLP could not be run.}} 
\label{tabla:resultsT}
\end{table*}

@@

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_time.eps,width=7cm}
\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one). Plot shows that using categorical variables as part of the dataset makes the problem hard to solve. As was expected, simpler methods are much faster to build the model than the complex ones.}}
\label{fig:time}
\end{center}
\end{figure}

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_rae.eps,width=7cm}
\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one). The M5P model obtains the lowest errors, whatever the dataset used.}}
\label{fig:rae}
\end{center}
\end{figure}

>>>>

Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager can eventually 
take them into account \cite{Armstrong2001,SThomassey2014}. 
                                % ¿Esto también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ
                                % [Pedro] esto iba referido a la Industria Editorial.
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they do? What are the results?

In this research, the problem of how many books should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for libraries, 
publishers and distributors. 
Usually, the company's expert sales managers analyzed historical data 
and applied their knowledge using external variables to calculate
appropriate predictions, for example, increasing or decreasing the 
sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.
%In any case, in general companies usually use a forecasting model and then, 
%an expert applies his knowledge, as the company might require an 
%interpretable and understandable model. 
However, carrying out the analysis and forecasting process as described,
may lead to an imprecise analysis and may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is large, and even, different experts can reach different
predictions from the same data set \cite{ChingChin2010,Sanders1994}.

@@

This is the new book sales forecasting case, a problem with issues such as 
dealing with limited data, finding adequate forecasting methods and selecting 
the best method to use \cite{ChingChin2010}.
In the case of new unpublished-books, there is no historical data to define 
patterns, and only some descriptive data about the new book is available 
\cite{ChingChin2010,FaderHardie2005,Madsen2008}.
Thus, not any timeseries-based forecasting method can be used \cite{Madsen2008,ChernWSF15}.

%This is the new book sales forecasting case, for which no historical data to make predictions is available \cite{ChingChin2010,FaderHardie2005,Madsen2008} and only some descriptive variables relative to the new unpublished-book are available.

%Forecasting sales of new books is a problem with issues such as dealing with limited data, finding adequate forecasting methods and selecting the best method to use \cite{ChingChin2010}.

%In the case of already published books, available historical data might help to generate predictive models.
%However, in the case of new books there is no historical data to define patterns, and only some descriptive data about the new book is available. 
%In these cases not any timeseries-based forecasting method can be used \cite{Madsen2008,ChernWSF15}.

%An additional issue is the difficulty to compare our model with classical forecasting methods, such as time series prediction methods, since books do not have specific sales time series.

@@

The main issue of this paper is to forecast sales for 
unpublished books for which no historical data is available, just some
descriptive variables relative to the new book. In order to do that,
training data includes historical sales data for all books published
in Spain for several years, including those descriptive variables.

%%% Principio de párrafos a eliminar o mover a estado del arte.
%% Fin de párrafos a eliminar.
  % [pedro] eliminados

The initial data set, provided in the framework of a contract by
Trevenque Editorial, included 3159 books, and included descriptive information 
for each book, such as price, points of sale, subject, publisher, sales, returns, 
among other information.
Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
each book.

@@

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	      & MAE 		& RMSE 		& RAE (\%) & RRSE (\%) 		\\
\hline
  M5P 		& 24.24 $\pm$ 0.96    & 197.48  & 577.28  & 35.21    & 41.85  \\
\hline
  LR 		  & 3533.84 $\pm$ 178.38& 247.22 & 561.67  & 44.08    & 40.71    \\
\hline
  SVM 		& 5586.96 $\pm$ 139.71& 215.69  & 574.76  & 38.46    & 41.66  \\
\hline
  kNN 		& 0.02 $\pm$ 0.00     & 302.07 	& 924.94 	& 53.86 	 & 67.05 	\\
\hline
  MLP 		& - 	  & - 	& - 	& - 	& - 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the original dataset (16 variables per book). 
    In this case, due to the categorial variables, the MLP could not be run.}} 
\label{tabla:resultsT}
\end{table*}

@@

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_time.eps,width=11cm}
\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one). Plot shows that using categorical variables as part of the dataset makes the problem hard to solve. As was expected, simpler methods are much faster to build the model than the complex ones.}}
\label{fig:time}
\end{center}
\end{figure}

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_rae.eps,width=11cm}
\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one). The M5P model obtains the lowest errors, whatever the dataset used.}}
\label{fig:rae}
\end{center}
\end{figure}
